Flowchart of Current Algorithm

### 2008-10-12 docs/flowchart/paper.tex
split the density and enthalpy updates

\item Compute the edge states, $(\rho X_k)^{(1),\nph,\star}$ and $(\rho h)^{(1),\nph,\star},$
      for the conservative update of $(\rho X_k)$ and $(\rho h).$  Here we
      predict $\rho'$, $(\rho h)'$, and $X_k$ to the edges, using
      a second-order Taylor expansion in space and time, as described in
      paper II, Appendix A, using $\V = \uadvone+w_0^{\nph,\star} \er$.  
      We do not include the reaction terms in the enthalpy prediction, 
      since we accounted for them already in {\bf React State}. 
      We use the base state density, $\rho_0$, and base state enthalpy, $(\rho h)_0$,
      to convert these to edge states for $(\rho X_k)$ and $(\rho h)$. 
      We define $\rho^{(1),\nph,\star} = \sum_k (\rho X_k)^{(1),\nph,\star}.$  \MarginPar{we actually split these now, and do $\rho$ first, compute $\psi$, and then do $(\rho h)$}

\item Evolve $(\rho X_k)^{(1)} \rightarrow (\rho X_k)^{(2),\star}$ and
$(\rho h)^{(1)} \rightarrow (\rho h)^{(2),\star}$ without explicitly including the 
reaction terms,
\begin{eqnarray}
(\rho X_k)^{(2),\star} &=& (\rho X_k)^{(1)} 
 - \dt \; \left[ \nablab \cdotb \left( (\uadvone+w_0^{\nph,\star} \er)  
  (\rho X_k)^{(1),\nph,\star} \right) \right] \enskip , \\ \nonumber  \\
(\rho h)^{(2'),\star} &=& (\rho h)^{(1)} - \dt \; \left[ \nablab \cdotb \left( (\uadvone+w_0^{\nph,\star} \er)  
  (\rho h)^{(1),\nph,\star} \right) \right] \nonumber \\
&& + \dt \; \left(\uadvone \cdotb \er\right) \left(\frac{\partial p_0}{\partial r} \right)^{n} 
+ \dt \; \psi^{\nmh} \enskip , \\
\rho^{(2'),\star} &=& \sum_k (\rho X_k)^{(2),\star} \enskip , \\ 
X_k^{(2),\star} &=& (\rho X_k)^{(2),\star} / \rho^{(2),\star}
\end{eqnarray}
\MarginPar{why $\rho^{(2'),\star}$ and not $\rho^{(2),\star}$?}
\item {\bf Correct Base}$(\rho_0^{(2),\star}, \etarho^{\nmh}) \rightarrow (\rho_0^{n+1,\star})$.

@@

@@

\item Compute the edge states, $(\rho X_k)^{(1),\nph}$ and $(\rho h)^{(1),\nph},$
      for the conservative update of $(\rho X_k)$ and $(\rho h).$  Here we
      predict $\rho'$, $(\rho h)'$, and $X_k$ to the edges, using
      a second-order Taylor expansion in space and time, as described in
      paper II, Appendix A, using $\V = \uadvtwo+w_0^{\nph} \er$. 
      Again, we do not include the reaction terms in the enthalpy prediction 
      since we accounted for them already in {\bf React State}.
      We use the base state density, $\rho_0$, and base state enthalpy, $(\rho h)_0$,
      to convert these to edge states for $(\rho X_k)$ and $(\rho h)$. 
      We define $\rho^{(1),\nph} = \sum_k (\rho X_k)^{(1),\nph}.$ \MarginPar{we split this into two now}

\item Evolve $(\rho X_k)^{(1)} \rightarrow (\rho X_k)^{(2)}$ and
$(\rho h)^{(1)} \rightarrow (\rho h)^{(2)},$ 
\begin{eqnarray}
(\rho X_k)^{(2)} &=& (\rho X_k)^{(1)} 
- \dt \; \left[ \nablab \cdotb \left( (\uadvtwo+w_0^{\nph} \er)  
(\rho X_k)^{(1),\nph} \right) \right]  \enskip , \\ \nonumber \\
(\rho h)^{(2')} &=& (\rho h)^{(1)} - \dt \; \left[ \nablab \cdotb \left( (\uadvtwo+w_0^{\nph} \er)  
(\rho h)^{(1),\nph} \right) \right] \nonumber \\
&& + \frac{\dt}{2} \; \left(\uadvtwo \cdotb \er\right)
\left [ \left(\frac{\partial p_0}{\partial r} \right)^{n}
      + \left(\frac{\partial p_0}{\partial r} \right)^{n+1}  \right ] 
+ \dt \; \psi^{\nph,\star} \enskip , \\ 
\rho^{(2')} &=& \sum_k (\rho X_k)^{(2)} \enskip , \\
X_k^{(2)} &=& (\rho X_k)^{(2)} / \rho^{(2)}
\end{eqnarray}

@@

>>>>

\item Compute the species edge states, $(\rho X_k)^{(1),\nph,\star}$,
  for the conservative update of $(\rho X_k)$.  Here we predict
  $\rho'$ and $X_k$ to the edges, using a second-order Taylor
  expansion in space and time, as described in paper II, Appendix A,
  using $\V = \uadvone+w_0^{\nph,\star} \er$.  We use the base state
  density, $\rho_0$, to convert these to edge states for $(\rho X_k)$.
  We define $\rho^{(1),\nph,\star} = \sum_k (\rho
  X_k)^{(1),\nph,\star}.$

\item Evolve $(\rho X_k)^{(1)} \rightarrow (\rho X_k)^{(2),\star}$
  without explicitly including the reaction terms,
\begin{eqnarray}
(\rho X_k)^{(2),\star} &=& (\rho X_k)^{(1)} 
 - \dt \; \left[ \nablab \cdotb \left( (\uadvone+w_0^{\nph,\star} \er)  
  (\rho X_k)^{(1),\nph,\star} \right) \right] \enskip , \\ \nonumber  \\
\rho^{(2'),\star} &=& \sum_k (\rho X_k)^{(2),\star} \enskip , \\ 
X_k^{(2),\star} &=& (\rho X_k)^{(2),\star} / \rho^{(2),\star}
\end{eqnarray}
\MarginPar{why $\rho^{(2'),\star}$ and not $\rho^{(2),\star}$?}

@@

\item Compute the enthalpy edge state, $(\rho h)^{(1),\nph,\star},$
  for the conservative update of $(\rho h).$ Here we predict $(\rho
  h)'$ to the edges, using a second-order Taylor expansion in space
  and time, as described in paper II, Appendix A, using $\V =
  \uadvone+w_0^{\nph,\star} \er$.  We do not include the reaction
  terms in the enthalpy prediction, since we accounted for them
  already in {\bf React State}.  We use the base state enthalpy,
  $(\rho h)_0$, to convert this to an edge state for $(\rho h)$.

\item Evolve $(\rho h)^{(1)} \rightarrow (\rho h)^{(2),\star}$ without
  explicitly including the reaction terms,
\begin{eqnarray}
(\rho h)^{(2'),\star} &=& (\rho h)^{(1)} - \dt \; \left[ \nablab \cdotb \left( (\uadvone+w_0^{\nph,\star} \er)  
  (\rho h)^{(1),\nph,\star} \right) \right] \nonumber \\
&& + \dt \; \left(\uadvone \cdotb \er\right) \left(\frac{\partial p_0}{\partial r} \right)^{n} 
+ \dt \; \psi^{\nmh} \enskip , 
\end{eqnarray}

\item {\bf Correct Base}$(\rho_0^{(2),\star}, \etarho^{\nmh}) \rightarrow (\rho_0^{n+1,\star})$.

@@

\item Compute the species edge states, $(\rho X_k)^{(1),\nph}$, for
  the conservative update of $(\rho X_k)$. Here we
  predict $\rho'$ and $X_k$ to the edges, using a second-order Taylor
  expansion in space and time, as described in paper II, Appendix A,
  using $\V = \uadvtwo+w_0^{\nph} \er$.  We use the base state
  density, $\rho_0$, to convert these to edge states for $(\rho X_k)$
  and $(\rho h)$.  We define $\rho^{(1),\nph} = \sum_k (\rho
  X_k)^{(1),\nph}$.

\item Evolve $(\rho X_k)^{(1)} \rightarrow (\rho X_k)^{(2)}$ 
without explicitly including the reaction terms,
\begin{eqnarray}
(\rho X_k)^{(2)} &=& (\rho X_k)^{(1)} 
- \dt \; \left[ \nablab \cdotb \left( (\uadvtwo+w_0^{\nph} \er)  
(\rho X_k)^{(1),\nph} \right) \right]  \enskip , \\ \nonumber \\
\rho^{(2')} &=& \sum_k (\rho X_k)^{(2)} \enskip , \\
X_k^{(2)} &=& (\rho X_k)^{(2)} / \rho^{(2)}
\end{eqnarray}

@@

\item Compute the enthalpy edge state, $(\rho h)^{(1),\nph}$, for the
  conservative update of $(\rho h)$. Here we predict $(\rho h)'$ to
  the edges, using a second-order Taylor expansion in space and time,
  as described in paper II, Appendix A, using $\V =
  \uadvtwo+w_0^{\nph} \er$.  Again, we do not include the reaction
  terms in the enthalpy prediction since we accounted for them already
  in {\bf React State}. We use the base state enthalpy, $(\rho h)_0$,
  to convert these to edge states for $(\rho h)$.

\item Evolve $(\rho h)^{(1)} \rightarrow (\rho h)^{(2)}$ 
without explicitly including the reaction terms,
\begin{eqnarray}
(\rho h)^{(2')} &=& (\rho h)^{(1)} - \dt \; \left[ \nablab \cdotb \left( (\uadvtwo+w_0^{\nph} \er)  
(\rho h)^{(1),\nph} \right) \right] \nonumber \\
&& + \frac{\dt}{2} \; \left(\uadvtwo \cdotb \er\right)
\left [ \left(\frac{\partial p_0}{\partial r} \right)^{n}
      + \left(\frac{\partial p_0}{\partial r} \right)^{n+1}  \right ] 
+ \dt \; \psi^{\nph,\star} \enskip ,
\end{eqnarray}
